---
title: "Competition_Analysis"
author: "Nathan Brandt"
date: "2/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters
* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed
  
#1) Multi-samples over time maintained at steady-stat in Ammonium-Sulfate Limited Media in the Mini-Stats analyzed on the Accuri.
#    Competitions-
#     Vessel 01 - R1-11 : Single Colony 11 from evloved population R1
#     Vessel 02 - R2-5 : Single Colony 5 from evloved population R2
#     Vessel 03 - R3-10 : Single Colony 10 from evloved population R3
#     Vessel 04 - GAT1-1 : GAT1-1 
#     All vs. DGY500

******
##Step 1: Load relevant libraries 

```{r}
# This is a function that just makes sure you have a package, or installs it for you without prompting

requireInstall <- function(packageName,isBioconductor=F) {
  if ( !try(require(packageName,character.only=T)) ) {
    print(paste0("You don't have ",packageName," accessible, ",
      "I'm gonna install it"))
    if (isBioconductor) {
      source("http://bioconductor.org/biocLite.R")                        
      biocLite(packageName)                                                 
    } else {
      install.packages("packageName", repos = "http://cran.us.r-project.org")
    }
  }
  return(1)
}

#Load libraries
requireInstall("flowCore",isBioconductor=T)
requireInstall("tidyverse")
requireInstall("googlesheets")
```

###Step 2: Read in all .fcs files in current directory and a sample sheet that contains four columns with 
* column1 = Well
* column2 = Experiment
* column3 = Strain(s)

```{r}
path = "/Users/Brandt/Google Drive/GAT1 evolution paper/Additional_Exp/Accuri_Data/"
folder_list <- gs_read(ss = gs_title("Experiment_Folder_List"))

for(x in 1:length(folder_list$Folders)) {
  if(x <= 1) {
    folder = folder_list[x,]
    sample_filename = paste("SampleSheet_", folder, sep = "" )
    
    sample_sheet <- gs_read(ss = gs_title(sample_filename))

    flowData <- read.flowSet(path = paste(path, folder, sep = ""), pattern = ".fcs", alter.names=TRUE)

    #Adds unique name to the flowFrames and adds sample sheet data to the pData of the flowset
    sampleNames(flowData) <- sample_sheet$Experiment
    pData(flowData)$Well <- sample_sheet$Well
    pData(flowData)$Strain <- sample_sheet$Strain
  } else {
    folder = folder_list[x,]
    sample_filename = paste("SampleSheet_", folder, sep = "" )
    
    sample_sheet <- gs_read(ss = gs_title(sample_filename))

    flowData_temp <- read.flowSet(path = paste(path, folder, sep = ""), pattern = ".fcs", alter.names=TRUE)

    #Adds unique name to the flowFrames and adds sample sheet data to the pData of the flowset
    sampleNames(flowData_temp) <- sample_sheet$Experiment
    pData(flowData_temp)$Well <- sample_sheet$Well
    pData(flowData_temp)$Strain <- sample_sheet$Strain
    #Combine FlowSets
    flowData <- rbind2(flowData, flowData_temp)
  }

}
```

#Transfer data into a dataframe and produce summary stats
```{r}
#Summary Statistics of Normalized Filtered Data
#Move filtered data into a dataframe
filter.data <- data.frame(FSC.A=NA,SSC.A=NA,FL1.A=NA,WELL=NA,STRAIN=NA)
stats.data <- data.frame(WELL=NA,STRAIN=NA,COUNT=NA,MEDIAN=NA,MEAN=NA,SD=NA,VAR=NA)